Analysis-ready VCF at Biobank scale using Zarr

### 2025-01-21 paper.tex
Update text for subset compute

We illustrate this cost of row-wise encoding in
Fig~\ref{fig-subset-matrix-compute}, where we run the af-dist calculation
on a small fixed-size subset of the genotype matrices of
Fig~\ref{fig-data-storage}. The two-dimensional chunking of Zarr
means that this sub-matrix can be efficiently
extracted, and therefore the execution time depends very weakly on 
the overall dataset size, with the computation requiring around
1 second for 1 million samples. Because of their 
row-wise encoding, CPU time scales with the number of samples
for all the other methods.
Fig~\ref{fig-subset-matrix-compute-supplemental} shows performance
for the same operation when selecting half of the samples in the 
dataset.

>>>>

We illustrate this cost of row-wise encoding in
Fig~\ref{fig-subset-matrix-compute}, where we run the af-dist calculation
on a small fixed-size subset of the genotype matrices of
Fig~\ref{fig-data-storage}. The two-dimensional chunking of Zarr
means that this sub-matrix can be efficiently
extracted, and therefore the execution time depends very weakly on 
the overall dataset size, with the computation requiring around
2 seconds for 1 million samples. Because of their 
row-wise encoding, CPU time scales with the number of samples
for all the other methods.
Fig~\ref{fig-subset-matrix-compute-supplemental} shows performance
for the same operation when selecting half of the samples in the 
dataset.
